### 2023-09-15 main.tex
sdf

The aim of this section is studying some extension to the analysis previously done when integrability property is lost. 
In particular, Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$. For the sake of simplicity we still study the geometry of chain and we provide the following extensions: 

@@

	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we can define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Subsection \ref{Subsection-Thermalized}.

@@

We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The generator reads

@@

where at the boundaries 

@@

while the bulk generator is 
This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space

@@

with absorbing boundaries, i.e. 

@@

The dual process has absorbing boundaries, i.e. all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability. This implies that, the chain is eventually void and the steady state correlation of the original process can be written via the absorption probabilities of the dual process as explained in the following. 
We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$. We assume that it is initially distribute with a configuration $\bm{n}$. For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$  and $s_{x}\in \{1,\ldots,N-1\}$ for every $x\in \{1,\ldots,m-1\}$. The following chain of equalities holds

@@

and where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}. Here, we denote by $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{1,\ldots,N-1\}$ absorbed at left, thus we denote by $|\hat{\xi}_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\

@@

Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$. This expectation is computed by \eqref{ExptationSS} once the absorption probabilities is known. The issue is that these absorption probabilities fulfil some difference equations that are not easy to solve. For example, we report here the solution for the one points correlations. 

@@

We have that $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 

@@

@@

we want to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries. Therefore, this $\mathcal{P}(1,\delta_{s}^{y})$ fulfils the following equations 

@@

where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$. The equations \eqref{gamblers-ruin} can be solved. Therefore, using \eqref{OnePtsCORR} and $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain 

@@

The right boundary generator is defined in a similar way. The $\alpha$'s are replaced by $\beta$'s and the action is only on site $L$. 

@@

where $\mathcal{L}^{TH}_{x,x+1}$ is \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$, i.e. 

@@

and similarly $\widetilde{\mathcal{L}}_{right}^{TH}$. 
The duality function is 

>>>>

In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
The aim of this section is studying some extension to the analysis previously done when integrability property is lost. We fix $\nu>1$ and, for the sake of simplicity, we still study the geometry of chain. We provide the following extensions: 

@@

	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Also for this thermalized process we prove duality. Subsection \ref{Subsection-Thermalized}.

@@

We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space $\Omega=\bigtimes_{x=1}^{L} \Omega_{x}$ and the generator reads

@@

The bulk is 
while at the boundaries 

@@

This process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space

@@

where the boundaries are absorbing, i.e. 

@@

The dual process has absorbing boundaries, i.e. all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability. This implies that, the chain is eventually voided and the steady state correlation of the original process can be written via the absorption probabilities of the dual process as explained in the following. 
We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$. We assume that it is initially distribute with a configuration $\bm{n}$. For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$  and $s_{x}\in \{1,\ldots,N-1\}$ for every $x\in \{1,\ldots,m\}$. The following chain of equalities holds

@@

 are called the \textit{absorption probabilities}, i.e. the probabilities that $i_{a}$ particles of species $a$ are absorbed at $0$ and $|\xi_{a}|-i_{a}$ are absorbed at $L+1$ when time goes to infinity and starting from a configuration $\hat{\bm{\xi}}$. Here we denoted $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$.

@@

Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations among non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$. This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities is known. The issue is that these absorption probabilities fulfil some difference equations that are not easy to solve. For example, we report here the solution for the one points correlations. 

@@

We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 

@@

The average occupation reads

@@

To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$. This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation

@@

where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$. The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain 

@@

The right boundary generator is defined in a similar way, where $\alpha$'s are replaced by $\beta$'s and the action is only on site $L$. 

@@

where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$, i.e. 

@@

and similarly $\widetilde{\mathcal{L}}_{right}^{TH}$, but acting on the site $L$. 
The duality function is the same, i.e.
